\documentclass[10pt,a4paper]{article}

\usepackage[a-1b]{pdfx}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=0.2in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{mathptmx}
\usepackage{titlesec}
\usepackage{paracol}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage[most]{tcolorbox}
\usepackage[normalem]{ulem}

\input{glyphtounicode}

\pdfgentounicode=1

\titleformat{\section}[frame]{\huge\bfseries}{}{.2em}{}

\titleformat{\subsection}{\large\bfseries}{-}{0.5em}{}

\titlespacing*{\subsection}
{0pt}{.05ex}{.05ex}

\definecolor{aliceblue}{rgb}{0.98, 0.98, 1}
%\definecolor{aliceblue}{rgb}{1, 1, 1}

\pagecolor{aliceblue}

\renewcommand{\maketitle}
{
	\begin{flushleft}
		\textbf{\Huge\theauthor}
	\end{flushleft}
	\begin{flushleft}
		\small{\textbf{{\faMapMarker} \hspace{0.2cm} Gainesville, Fl} \hspace{2.5cm} \textbf{{\faMobile} \hspace{0.2cm} +1 (352)--226--1217} \\
				\textbf{{\faEnvelope} \hspace{0.1cm} naman.arora@tutanota.com} \hspace{0.5cm}
				\textbf{{\faGithub} \hspace{0.1cm} \href{https://github.com/r0ck3r008}{https://github.com/r0ck3r008}}}
	\end{flushleft}
}

\titleformat{\section}
{\Large}
{}{0em}
{}
[\titlerule]

\begin{document}

\title{Resume}
\author{Naman Arora}
\maketitle


\section{{\faUser} About Me}
\begin{flushleft}
	I am a passionate Systems Developer with keen interest in all things Databases, Networking, Operating Systems and Cybersecurity. From concurrent RDBMS to privacy protecting overlay networks, I develop innovative systems to tackle the fundamental engineering problems with my 4+ years of experience in C/C++ and GNU/Linux systems.
\end{flushleft}

%\section{Education}
\section{{\faUniversity} Education}

\begin{itemize}[noitemsep,nolistsep]
	\item\textbf{Pursuing Masters in Computer and Information Sciences} \hfill \textit{August 2019 - Present}
		\begin{itemize}[leftmargin=*]
			\setlength\itemsep{-0.25em}
			\item[$\ast$]\textbf{Ongoing GPA 3.53/4.00 from University Of Florida, Gainesville}
			\item[$\ast$]Highlighted Coursework: Database System Implementation, Distributed Operating Systems, Blockchain
		\end{itemize}
	\item\textbf{Bachelor of Technology in Computer Science and Engineering} \hfill \textit{July 2015 - May 2019}
		\begin{itemize}[leftmargin=*]
			\setlength\itemsep{-0.25em}
			\item[$\ast$]\textbf{CGPA 8.3/10.0 from SRM Institute Of Science and Technology, Chennai, India}
			\item[$\ast$]Highlighted Coursework: Network Programming, Database Management Systems, Operating Systems
		\end{itemize}
\end{itemize}

%\section{Skills}
\section{{\faCogs} Skills}
	\begin{itemize}[noitemsep,nolistsep]
		\item\textbf{Programming/Scripting Languages:} C/C++, Go, Rust, Python, Java, SQL, lex/yacc
		\item\textbf{Programs and Frameworks:} Docker, PostgreSQL, Mariadb
		\item\textbf{Operating Systems:} GNU/Linux, Microsoft Windows, Android, OpenBSD
	\end{itemize}


\section{{\faNewspaperO} Publications}
	\begin{itemize}[noitemsep,nolistsep]
		\item{\textbf{A Relay for A SDN Controller}} \hfill \textit{February 2020}
			\begin{itemize}[leftmargin=*]
				\setlength\itemsep{-0.25em}
				\item[$\ast$]Patent Application No. 202041008146 Ref: P/19/2116 (CS.9.18) dated 10.08.19, Indian Patent Act, 1970
				\item[$\ast$]With co-inventors Ms. Vaishnavi Moorthy, Dr. Revathi Venkataraman, Nikhil Gupta
			\end{itemize}
		\item{\textbf{An Attendance System and Method Thereof}} \hfill \textit{December 2018}
			\begin{itemize}[leftmargin=*]
				\setlength\itemsep{-0.25em}
				\item[$\ast$]``Patent Office Journal dated 27th July 2018'', page No. 28230, Indian Patent Act, 1970
				\item[$\ast$]With co-inventors Ms. M. Gayathri, Dr. C. Malathy and Rakshit Jain
			\end{itemize}
	\end{itemize}

\section{{\faCoffee} Projects}
	\begin{itemize}[noitemsep,nolistsep]

		\item{\textbf{\href{https://github.com/r0ck3r008/database-from-scratch}{DFS: A Database Engine Written from Scratch}} \hfill \textit{April 2020}}
			\begin{itemize}[leftmargin=*]
				\setlength\itemsep{-0.25em}
				\item[$\ast$]\textit{Linux, C++, Database Systems Implementation, flex/yacc}
				\item[$\ast$]Database engine capable of processing \textbf{1GB+ or 7,000,000+ records.}
				\item[$\ast$]Complete with aggregate, join and select functionalities
			\end{itemize}

		\item{\textbf{\href{https://github.com/r0ck3r008/arch-perf-benchmark}{A Performance Benchmark of Image Encryption Algorithms}} \hfill \textit{December 2019}}
			\begin{itemize}[leftmargin=*]
				\setlength\itemsep{-0.25em}
				\item[$\ast$]\textit{C, Python, Image Encryption, Computer Architecture, RV8}
				\item[$\ast$]Compares simulated \textbf{RISC-V, ARM and x86 ISA}
				\item[$\ast$]Image encryption benchmark framework \textbf{for RC4, Chirikov and Vigenere algorithms}.
			\end{itemize}

		\item{\textbf{\href{https://github.com/r0ck3r008/twitter-engine}{Twitter Engine for Highly Concurrent Systems}} \hfill \textit{December 2019}}
			\begin{itemize}[leftmargin=*]
				\setlength\itemsep{-0.25em}
				\item[$\ast$]\textit{Elixir, Phoenix Framework, Websockets}
				\item[$\ast$]Distributed and Fault tolerant Twitter Engine \textbf{tested with 100,000 simultaneous user processes.}
			\end{itemize}

		\item{\textbf{\href{https://github.com/r0ck3r008/tapestry\_p2p}{Tapestry: A P2P Distributed Hash Table Network}} \hfill \textit{November 2019}}
			\begin{itemize}[leftmargin=*]
				\setlength\itemsep{-0.25em}
				\item[$\ast$]\textit{Elixir, P2P Networking, DHT}
				\item[$\ast$]Resilient P2P network capable of \textbf{connecting 2,000+ clients with reliable resource sharing.}
				\item[$\ast$]Reliable resource sharing \textbf{even with 20\% failed nodes.}
			\end{itemize}

	\end{itemize}

\end{document}
